Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-12 paper/main.tex
Added more text to results and brushed on Conclusion adding future work

The sum of the amount of time it took for the underlying hash library to
calculate the hash operations are exhibited in Figures \ref{fig:graph:10001b},
\ref{fig:graph:1001kb}, \ref{fig:graph:501mb}, \ref{fig:graph:5100mb} and
\ref{fig:graph:11gb}. We call this \emph{time spent hashing}.

@@

BLAKE, \ac{BMW}, Shabal and Simd outperforms \ac{SHA}-256 when both uploading
and downloading a 1GB file. The difference between the slowest (JH) and the
fastest (BLAKE) algorithm is 229.92s when uploading the one gigabyte file.

@@

We had hoped to contribute more to the Open Source project Tahoe-LAFS, when
starting on our assignment. It was early evident that implementing a new
capability was out of scope, since creating Python bindings and trying out
new implementations was prioritized.

@@

Perhaps the most important finding in this project, is that the SUPERCOP
benchmarking indeed drives the development of new and better implementations
forward, but since the SUPERCOP \ac{API} does not conform to the \ac{NIST}
\ac{API}, the developers leave important functionality out (i.e.
{\verb update() }), and hence make it difficult for people who wish to try out
and test the remaining \ac{SHA}-3 candidates.

>>>>

The sum of the amount of time it took for the underlying hash library to
calculate the hash operations are exhibited in Figures \ref{fig:graph:10001b},
\ref{fig:graph:1001kb}, \ref{fig:graph:501mb}, \ref{fig:graph:5100mb} and
\ref{fig:graph:11gb}. We call this \emph{Time spent hashing}.

@@

BLAKE, \ac{BMW}, Shabal and Simd outperforms \ac{SHA}-256 when both uploading
and downloading a 1GB file, but on small files, SHA-256 is faster by a large
margin. The difference between the slowest (JH) and the fastest (BLAKE)
algorithm is 229.92s when uploading the one gigabyte file.

@@

We had hoped to contribute more to the Open Source project Tahoe-LAFS, when
starting on our assignment. It was early evident that implementing a new
capability was out of scope, since creating Python bindings and trying out
new implementations was prioritized. Future work should implement the support
for choosing hashing algorithm in a proper manner which ensures backwards
compatibility.

@@

Perhaps the most important finding in this project, is that the SUPERCOP
benchmarking indeed drives the development of new and better implementations
forward, but since the SUPERCOP \ac{API} does not conform to the \ac{NIST}
\ac{API}, the developers leave important functionality out (i.e.
{\verb update() }), and hence make it difficult for people who wish to try out
and test the \ac{SHA}-3 candidates in real world applications.
